Structured Versus Decorated Cospans

### 2022-04-07 cospans_compositionality_3.tex
fixed bibliography

\bibitem{AP} AlgebraicPetri team, GitHub repository. Available at
\href{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}.

\bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
algebraic framework for structured epidemic modeling.   Available at \href{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}.

\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.   Available as \href{http://arxiv.org/abs/1911.04630}{arXiv:1911.04630}.

\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in circuit theory, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 727--783.    Available as \href{https://arxiv.org/abs/1707.08321}{arXiv:1707.08321}.

\bibitem{BE} J.\ C.\ Baez and J.\ Erbele, Categories in control, \textsl{Theory Appl.\ Categ.} {\bf 30} (2015), 836--881. Available as \href{http://arxiv.org/abs/1405.6881}{arXiv:1405.6881}.

\bibitem{BF}  J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1158--1222.  Available as \href{http://arxiv.org/abs/1504.05625}{arXiv:1504.05625}.

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, 
\textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}. Available as 
\href{http://arxiv.org/abs/1508.06448}{arXiv:1508.06448}.

\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341. 
\href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
Available as 
\href{https://arxiv.org/abs/1808.05415}{arXiv:1808.05415}.

\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for chemical reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.
Available as \href{http://arxiv.org/abs/1704.02051}{arXiv:1704.02051}.

\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory, \textsl{ACM Trans.\ 
Cyber-Phys.\ Syst.\ } \textbf{5} (2021). \href{https://doi.org/10.1145/3461669}{https://doi.org/10.1145/3461669}. Available as 
\href{https://arxiv.org/abs/2010.08003}{arXiv:2010.08003}.

\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, 
eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Available at 
\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.

@@

\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \textsl{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027. Available as \href{https://arxiv.org/abs/1605.08100}{arXiv:1605.08100}.

\bibitem{CourserThesis} K.\ Courser, \textsl{Open Systems: a Double Categorical Perspective}, Ph.D.\ thesis, Department of Mathematics, U.\ C.\ Riverside, 2020.  Available as \href{https://arxiv.org/abs/2008.02394}{arXiv:2008.02394}.

@@

\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  Available as 
\href{http://arxiv.org/abs/1502.00872}{arXiv:1502.00872}.

\bibitem{FongThesis} B.\ Fong, \textsl{The Algebra of Open and Interconnected Systems},
Ph.D.\ thesis, Computer Science Department, University of Oxford, 2016.
Available as \href{https://arxiv.org/abs/1609.05382}{arXiv:1609.05382}.

\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings 
of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10. 
\href{https://doi.org/10.1145/2933575.2934556}{https://doi.org/10.1145/2933575.2934556}. Available as 
\href{http://arxiv.org/abs/510.05076}{arXiv:1510.05076}.

@@

\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.  Available as \href{https://arxiv.org/abs/1910.09240}{arXiv:1910.09240}.

@@

\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.

@@

\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986.  Available at \href{https://tinyurl.com/state}{https://tinyurl.com/state-}  \href{https://tinyurl.com/state-categories}{categories}.

@@

\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1159--1207. Available as \href{https://arxiv.org/abs/1809.00727}{arXiv:1809.00727}.

\bibitem{Niefield} S.~Niefield, Span, cospan, and other double categories, \textsl{Theory Appl.\ Categ.} \textbf{26} (2012), 729--742. Available as \href{https://arxiv.org/abs/1201.3789}{arXiv:1201.3789}.

\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981.

\bibitem{PollardThesis} B.\ S.\ Pollard, \textsl{Open Markov Processes and Reaction Networks}, Ph.D. thesis, Department of Physics, U. C. Riverside, 2017.  Available as \href{https://arxiv.org/abs/1709.09743}{arXiv:1709.09743}.

@@

\bibitem{Riehl} E.\ Riehl, \textsl{Category Theory In Context}, Dover Publications, New York, 2016. Available at \href{https://math.jhu.edu/~eriehl/context/}{https://math.jhu.edu/~eriehl/context/}.

\bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57. 
\href{https://doi.org/10.1007/s10485-019-09565-x}{https://doi.org/10.1007/s10485-019-09565-x}.
Available as \href{https://arxiv.org/abs/1609.08086}{arXiv:1609.08086}.

\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.\ Categ.\ }\textbf{20} (2008), 650--738. Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.

@@

\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.   Available as \href{http://arxiv.org/abs/1301.1053}{arXiv:1301.1053}.

\bibitem{VSL} D.\ Vagner, D.\ Spivak and E.\ Lerman, Algebras of open dynamical systems on the operad of wiring diagrams, \textsl{Theory Appl.\ Categ.\ } \textbf{30} (2015), 1793--1822. Available as \href{https://arxiv.org/abs/1408.1598}{arXiv:1408.1598}.

>>>>

\bibitem{AP} AlgebraicPetri team, GitHub repository. 
\href{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}{https://github.com/AlgebraicJulia/AlgebraicPetri.jl}.

\bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
algebraic framework for structured epidemic modeling.  \href{https://doi.org/10.48550/arxiv.2203.16345}{https://doi.org/10.48550/arxiv.2203.16345}.

\bibitem{BC} J.\ C.\ Baez and K.\ Courser, Structured cospans,  \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1771--1822.    	\href{https://doi.org/10.48550/arXiv.1911.04630}{https://doi.org/10.48550/arXiv.1911.04630}.

\bibitem{BCR} J.\ C.\ Baez, B.\ Coya and F.\ Rebro, Props in network theory, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 727--783.    	\href{https://doi.org/10.48550/arXiv.1707.08321}{https://doi.org/10.48550/arXiv.1707.08321}.

\bibitem{BE} J.\ C.\ Baez and J.\ Erbele, Categories in control, \textsl{Theory Appl.\ Categ.} {\bf 30} (2015), 836--881.  \href{https://doi.org/10.48550/arXiv.1405.6881}{https://doi.org/10.48550/arXiv.1405.6881}.

\bibitem{BF}  J.\ C.\ Baez and B.\ Fong, A compositional framework for passive linear networks, \textsl{Theory Appl.\ Categ.\ }\textbf{33} (2018), 1158--1222.  \href{https://doi.org/10.48550/arXiv.1504.05625}{https://doi.org/10.48550/arXiv.1504.05625}.

\bibitem{BFP} J.\ C.\ Baez, B.\ Fong and B.\ S.\ Pollard, A compositional framework for Markov processes, \textsl{Jour. Math. Phys.} \textbf{57} (2016), 033301. 
\href{https://doi.org/10.1063/1.4941578}{https://doi.org/10.1063/1.4941578}.

\bibitem{BM}  J.\ C.\ Baez and J.\ Master, Open Petri nets, \textsl{Math.\ Struct.\ Comput.\ Sci.\ }\textbf{30} (2020), 314--341.  \href{https://doi.org/10.1017/s0960129520000043}{https://doi.org/10.1017/s0960129520000043}.
Also available at
\href{https://doi.org/10.1017/S0960129520000043}{https://doi.org/10.1017/S0960129520000043}.

\bibitem{BP} J.\ C.\ Baez and B.\ S.\ Pollard, A compositional framework for reaction networks, \textsl{Rev.\ Math.\ Phys.\ }\textbf{29} 
(2017), 1750028. \href{https://doi.org/10.1142/S0129055X17500283}{https://doi.org/10.1142/S0129055X17500283}.   Also available at 
\href{https://doi.org/10.48550/arXiv.1508.06448}{https://doi.org/10.48550/arXiv.1508.06448}.

\bibitem{BFV} G.\ Bakirtzis, C.\ H.\ Fleming and C.\ Vasilakopoulou, Categorical semantics of cyber-physical systems theory, \textsl{ACM Trans.\ 
Cyber-Phys.\ Syst.\ } \textbf{5} (2021). \href{https://doi.org/10.1145/3461669}{https://doi.org/10.1145/3461669}.   Also available at \href{https://doi.org/10.48550/arXiv.2010.08003}{https://doi.org/10.48550/arXiv.2010.08003}.

\bibitem{BSZ} F.\ Bonchi, P.\ Soboci\'nski and F.\ Zanasi, A categorical semantics of signal flow graphs, in \textsl{CONCUR 2014--Concurrency Theory}, 
eds.\ P.\ Baldan and D.\ Gorla, Lecture Notes in Computer Science \textbf{8704}, Springer, Berlin, 2014, pp.\ 435--450. 
\href{https://doi.org/10.1007/978-3-662-44584-6\_30}{https://doi.org/10.1007/978-3-662-44584-6\_30}.  Also available at 
\href{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}{http://users.ecs.soton.ac.uk/ps/papers/sfg.pdf}.

@@

\bibitem{Courser} K.\ Courser, A bicategory of decorated cospans, \textsl{Theory Appl.\ Categ.} \textbf{32} (2017), 995--1027.  \href{https://doi.org/10.48550/arXiv.1605.08100}{https://doi.org/10.48550/arXiv.1605.08100}

\bibitem{CourserThesis} K.\ Courser, \textsl{Open Systems: a Double Categorical Perspective}, Ph.D.\ thesis, Department of Mathematics, U.\ C.\ Riverside, 2020.  
\href{https://doi.org/10.48550/arXiv.2008.02394}{https://doi.org/10.48550/arXiv.2008.02394}.

@@

\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  \href{https://doi.org/10.48550/arXiv.1502.00872}{https://doi.org/10.48550/arXiv.1502.00872}.

\bibitem{FongThesis} B.\ Fong, \textsl{The Algebra of Open and Interconnected Systems},
Ph.D.\ thesis, Computer Science Department, University of Oxford, 2016.  \href{https://doi.org/10.48550/arXiv.1609.05382}{https://doi.org/10.48550/arXiv.1609.05382}

\bibitem{FRS} B.\ Fong, P.\ Rapisarda and P.\ Sobocinski, A categorical approach to open and interconnected dynamical systems, in \textsl{Proceedings 
of the 31st Annual ACM/IEEE Symposium on Logic in Computer Science (LICS)}, IEEE, New York, 2016, pp.\ 1--10. 
\href{https://doi.org/10.1145/2933575.2934556}{https://doi.org/10.1145/2933575.2934556}. Also available at
\href{https://doi.org/10.48550/arXiv.1510.05076}{https://doi.org/10.48550/arXiv.1510.05076}.

@@

\bibitem{HS}  L.\ W.\ Hansen and M.\ Shulman, Constructing symmetric monoidal bicategories functorially.  Available as \href{https://doi.org/10.48550/arXiv.1910.09240}{https://doi.org/10.48550/arXiv.1910.09240}.

@@

\bibitem{KSW} P.\ Katis, N.\ Sabadini and R.\ F.\ C.\ Walters, On the algebra of systems with feedback and boundary, \textsl{Rendiconti del Circolo Matematico di Palermo Serie II} \textbf{63} (2000), 123--156.   \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758&rep=rep1&type=pdf}{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.51.5758\&rep=rep1\&type=pdf}.

@@

\bibitem{Lawvere} F.\ W.\ Lawvere, State categories and response functors, unpublished manuscript, 1986.  \href{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}{https://github.com/mattearnshaw/lawvere/blob/master/pdfs/1986-state-categories-and-response-functors.pdf}

@@

\bibitem{MV} J.\ Moeller and C.\ Vasilakopoulou, Monoidal Grothendieck construction, \textsl{Theory Appl.\ Categ.\ }\textbf{35} (2020), 1159--1207.  \href{https://doi.org/10.48550/arXiv.1809.00727}{https://doi.org/10.48550/arXiv.1809.00727}.

\bibitem{Niefield} S.~Niefield, Span, cospan, and other double categories, \textsl{Theory Appl.\ Categ.} \textbf{26} (2012), 729--742.  \href{https://doi.org/10.48550/arXiv.1201.3789}{https://doi.org/10.48550/arXiv.1201.3789}.

\bibitem{Peterson} J.\ L.\ Peterson, \textit{Petri Net Theory and the Modeling of Systems}, Prentice-Hall, New Jersey, 1981. \href{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}{http://dl.icdst.org/pdfs/files3/2bf95f7fde49a09814231bbcbe592526.pdf}.

\bibitem{PollardThesis} B.\ S.\ Pollard, \textsl{Open Markov Processes and Reaction Networks}, Ph.D. thesis, Department of Physics, U. C. Riverside, 2017. \href{https://doi.org/10.48550/arXiv.1709.09743}{https://doi.org/10.48550/arXiv.1709.09743}.

@@

\bibitem{Riehl} E.\ Riehl, \textsl{Category Theory In Context}, Dover Publications, New York, 2016.  \href{https://math.jhu.edu/~eriehl/context/}{https://math.jhu.edu/~eriehl/context/}.

\bibitem{SSV} P.\ Schultz, D.\ Spivak and C.\ Vasilakopoulou, Dynamical systems and sheaves, \textsl{Appl.\ Cat.\ Struct.\ }\textbf{28} (2020), 1--57. 
\href{https://doi.org/10.1007/s10485-019-09565-x}{https://doi.org/10.1007/s10485-019-09565-x}.  Also available at \href{https://doi.org/10.48550/arXiv.1609.08086}{https://doi.org/10.48550/arXiv.1609.08086}.

\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.\ Categ.\ }\textbf{20} (2008), 650--738.  \href{https://doi.org/10.48550/arXiv.0706.1286}{https://doi.org/10.48550/arXiv.0706.1286}.

@@

\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.    \href{https://doi.org/10.48550/arXiv.1301.1053}{https://doi.org/10.48550/arXiv.1301.1053}.

\bibitem{VSL} D.\ Vagner, D.\ Spivak and E.\ Lerman, Algebras of open dynamical systems on the operad of wiring diagrams, \textsl{Theory Appl.\ Categ.\ } \textbf{30} (2015), 1793--1822. \href{https://doi.org/10.48550/arXiv.1408.1598}{https://doi.org/10.48550/arXiv.1408.1598}.
